Learning complex models with invertible neural networks: a likelihood-free Bayesian approach

### 2019-07-17 latex/paper_supplementary.tex
Add new version of text

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Regression_kl.png}
\caption{KL divergence ($D_{KL}$) between the true and estimated posteriors of the regression weights in our toy Bayesian regression example. The $D_{KL}$ is depicted at every $n$ observations used during training.} 
\end{figure}

@@

\subsubsection*{Summary network}
We use a bidirectional long short-term memory (LSTM) recurrent neural network \cite{gers1999learning} for summarizing the Ricker time-series into fixed-size vectors. The LSTM network architecture is a good choice for this example, as it is able to capture long-term in datasets with temporal or spatial autocorrelations. LSTMs can also easily deal with variable length time-series.

\subsubsection*{Simulation}
We place the following uniform priors over the Ricker model parameters:
\begin{align*}
\rho &\sim \mathcal{U}(0,15) \numberthis \\
r &\sim \mathcal{U}(1,90)  \numberthis \\
\sigma &\sim \mathcal{U}(0.05,0.7)  \numberthis 
\end{align*}
These ranges are very broad, as datasets generated by extreme parameter values appear implausible in real-world scenarios. Nevertheless, we stick to broad priors for training, even though parameter recovery might degrade at the extremes. Figure XXX depicts some Ricker datasets generated by parameters drawn from the specified prior.

@@

\subsubsection*{Simulation}
We place the following uniform priors over the two rate parameters of the stochastic SIR model:
\begin{align*}
\beta &\sim \mathcal{U}(0.01, 1) \numberthis \\
\gamma &\sim \mathcal{U}(0.01,\beta)  \numberthis 
\end{align*}
Figure XXX depicts some SIR datasets generated by parameters drawn from the specified priors.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Regression_kl.png}
\caption{KL divergence ($D_{KL}$) between the true and estimated posteriors of the regression coefficients in our toy Bayesian regression example. The $D_{KL}$ is depicted at every $n$ observations used during training.} 
\end{figure}

@@

\subsubsection*{Summary network}
We use a bidirectional long short-term memory (LSTM) recurrent neural network \cite{gers1999learning} for summarizing the Ricker time-series into fixed-size vectors. The LSTM network architecture is a reasonable choice for this example, as it is able to capture long-term dependencies in datasets with temporal or spatial autocorrelations. LSTMs can also easily deal with variable-length time-series.

\subsubsection*{Simulation}
We place the following uniform priors over the Ricker model parameters:
\begin{align*}
\rho &\sim \mathcal{U}(0,15) \numberthis \\
r &\sim \mathcal{U}(1,90)  \numberthis \\
\sigma &\sim \mathcal{U}(0.05,0.7)  \numberthis 
\end{align*}
These ranges appear to be very broad, as datasets generated by extreme parameter values appear implausible in real-world scenarios. Nevertheless, we stick to broad priors for training, even though parameter recovery might degrade at the extremes.

@@

\subsubsection*{Simulation}
We place the following uniform priors over the two rate parameters of the stochastic SIR model:
\begin{align*}
\beta &\sim \mathcal{U}(0.01, 1) \numberthis \\
\gamma &\sim \mathcal{U}(0.01,\beta)  \numberthis 
\end{align*}
